Modelling Prehistoric Iconographic Compositions. The \proglang{R} package \pkg{decorr}

### 2020-12-04 article_rvTH16.tex
huch

@@

\caption{\label{fig:figs}Concatenate of 'a', 'r' and 't' graphical units is 'art'}\label{fig:unnamed-chunk-1}
\end{figure}

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-2-1}

\caption{\label{fig:figs}Potential spatial relations between graphical units}\label{fig:unnamed-chunk-2}
\end{figure}

@@

The inventory of decorations is stored in the \code{imgs} dataframe. The field \code{imgs$idf} is the short name of the decoration, useful during statistical analysis. The primary key of each decoration is the concatenate of \code{imgs$site} and \code{imgs$decor}. These keys will allow joints with the other dataframes (\code{nodes} and \code{edges})\\
%
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:41 2020
\begin{table}[H]
\centering
\begin{tabular}{|p{0.5cm}|p{2.5cm}|p{2.5cm}|p{8.5cm}|}
  \hline
idf & site & decor & img \\ 
  \hline
  1 & Cerro Muriano & Cerro Muriano 1 & Cerro\_Muriano.Cerro\_Muriano\_1.jpg \\ 
    2 & Torrejon Rubio & Torrejon Rubio 1 & Torrejon\_Rubio.Torrejon\_Rubio\_1.jpg \\ 
    3 & Brozas & Brozas & Brozas.Brozas.jpg \\ 
    4 & Zarza de Montanchez & Zarza De Montanchez & Zarza\_de\_Montanchez.Zarza\_De\_Montanchez.jpg \\ 
    5 & Ibahernando & Ibahernando & Ibahernando.Ibahernando.jpg \\ 
   \hline
\end{tabular}
\caption{The studied corpus, the \code{imgs.tsv} dataframe} 
\label{Test_table}
\end{table}

%
The \pkg{decorr} package training dataset is composed by five stelaes decorations drawings \citep{DiazGuardamino10} belonging to the so-called 'Warrior stelae' family -- with about 140 stelae -- dated to the Late Bronze Age of SW Iberian peninsula \citep{Celestino01}. \\
At first the drawings dataset can be checked by using the \code{imgs} dataframe and the \pkg{magick} package (Fig. \ref{fig:timg})
%
\begin{kframe}
\begin{verbatim}
R> # library("magick")
R> pth <- system.file("extdata", package = "decorr")
R> imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
+                     sep="\t", stringsAsFactors = FALSE)
R> lims <- list()
R> for(i in 1:nrow(imgs)){
+    i1 <- image_read(paste0(pth,"\\",imgs[i,"img"]))
+    lbl.txt <- paste0(imgs[i,"idf"],"\n",
+                      imgs[i,"site"],"\n",
+                      imgs[i,"decor"],"\n",
+                      imgs[i,"img"],"\n",
+                      image_info(i1)$width,"*",image_info(i1)$height," px")
+    i1 <- image_annotate(i1,lbl.txt,location = "northwest",
+                         size = 25, color = "red")
+    lims[[length(lims)+1]]<- i1
+  }
R> out.img <- image_append(c(image_append(c(lims[[1]],lims[[2]],lims[[3]])),
+                            image_append(c(lims[[4]],lims[[5]]))),
+                          stack = TRUE)
R> plot(out.img)
\end{verbatim}
\end{kframe}\begin{figure}[H]

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Nodes (from \\code{nodes.csv} dataframe)}"
R> print(xtable::xtable(head(nodes),
+                       caption = caption),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:43 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 & personnage & 349.81 & -298.32 \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   2 & casque & 349.81 & -243.99 \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 & lance & 238.46 & -298.32 \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   4 & bouclier & 446.02 & -381.17 \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   5 & peigne & 283.00 & -358.01 \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   7 & sexe\_masculin & 342.69 & -427.49 \\ 
   \hline
\end{tabular}
\caption{Nodes (from \code{nodes.csv} dataframe)}} 
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Edges (from \\code{edges.csv} dataframe)}"
R> print(xtable::xtable(head(edges),
+                 caption=caption,
+                 label="edgesdf"),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:43 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrl}
  \hline
 & site & decor & a & b & type \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 &   4 & = \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   1 &   5 & = \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 &   5 & = \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   1 &   2 & + \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   1 &   7 & + \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   3 &   1 & = \\ 
   \hline
\end{tabular}
\caption{Edges (from \code{edges.csv} dataframe)}} 
\label{edgesdf}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> # par(mar=c(0.1,0.1,0.1,0.1))
R> # library("decorr")
R> # library("magick")
R> # imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
R> #                       sep="\t", stringsAsFactors = FALSE)
R> # nodes <- read.table(system.file("extdata", "nodes.tsv", package = "decorr"),
R> #                     sep="\t",stringsAsFactors = FALSE)
R> # edges <- read.table(system.file("extdata", "edges.tsv", package = "decorr"),
R> #                     sep="\t",stringsAsFactors = FALSE)
R> lgrph <- list_dec(imgs,nodes,edges,var="type")
R> plot(lgrph[[1]],
+       vertex.color = "orange",
+       vertex.frame.color="orange",
+       vertex.label.color = "black",
+       vertex.size = 8,
+       vertex.label.cex = 0.6,
+       edge.color = "orange",
+       vertex.label.family="Helvetica"
+  )
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/igraph-1}

\caption{\label{fig:figs}R interface. Plot of the first graph of the list}\label{fig:igraph}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> # library(decorr)
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".shp",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(nds.df[6,],
+                       caption="Sixth node of the Torrejon Rubio 1 decoration",
+                       label="nd",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:43 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrrrr}
  \hline
 & site & decor & id & type & x & y & coords.x1 & coords.x2 \\ 
  \hline
13 & Torrejon Rubio & Torrejon Rubio 1 &   6 & epee & 366.70 & -563.14 & 366.70 & -563.14 \\ 
   \hline
\end{tabular}
\caption{Sixth node of the Torrejon Rubio 1 decoration} 
\label{nd}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> # library(decorr)
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(eds.df[1,],
+                       caption="First edge of the Torrejon Rubio 1 decoration, the proximity between the sword (GU 6) and the fibula (GU 5)",
+                       label="eds.df",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:43 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrlrrrr}
  \hline
 & site & decor & a & b & type & xa & ya & xb & yb \\ 
  \hline
9 & Torrejon Rubio & Torrejon Rubio 1 &   6 &   5 & = & 366.70 & -563.14 & 490.12 & -513.24 \\ 
   \hline
\end{tabular}
\caption{First edge of the Torrejon Rubio 1 decoration, the proximity between the sword (GU 6) and the fibula (GU 5)} 
\label{eds.df}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> # library("decorr")
R> par(mar=c(0,0,0,0))
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> img.graph <- plot_dec_grph(nds.df = nds.df,
+                             eds.df = eds.df,
+                             site = sit,
+                             decor = dec,
+                             doss = system.file("extdata", package = "decorr"),
+                             lbl.txt = "type",
+                             lbl.size=2,
+                             shw = c("nodes","edges"))
R> plot(image_trim(img.graph))
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/tr_st-1}

\caption{\label{fig:figs}Torrejon Rubio 1 decoration}\label{fig:tr_st}
\end{figure}

@@

The \code{plot_nds_compar()}and \code{plot_eds_compar()} functions create a \code{.png} image of two or more decorations plotted side-by-side with common nodes or edges identified and returns the names of the images. The common edges or nodes are displayed in red by default.
Let us choose the decorations \code{1} (\emph{Cerro Muriano 1}) and \code{4} (\emph{Zarza de Montsanchez}) and identify common edges.

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> eds_compar <- plot_eds_compar(g.compar, c(1,4),
+                                doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unlist(listg, recursive = FALSE): object 'g.compar' not found}}\begin{verbatim}
R> plot(image_trim(image_read(eds_compar)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(eds\_compar): object 'eds\_compar' not found}}\end{kframe}

The comparison shows that \code{1} (\emph{Cerro Muriano 1}) and \code{4} (\emph{Zarza de Montsanchez}) decorations have two (2) common edges: \code{lance -=- personnage} and \code{personnage -=- bouclier}.

@@

\begin{kframe}
\begin{verbatim}
R> df.same_edges <- same_eds(lgrph,"type")
R> caption <- "Number of same edges between all decoration pairwise comparisons"
R> print(xtable::xtable(df.same_edges,
+                       caption = caption,
+                       label = "Test_table_2",
+                       size = 8,
+                       digits = c(0)),
+        table.placement="H",
+        include.rownames = TRUE)
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:47 2020
\begin{table}[H]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & 1 & 2 & 3 & 4 & 5 \\ 
  \hline
1 & 0 & 0 & 1 & 2 & 0 \\ 
  2 & 0 & 0 & 3 & 7 & 1 \\ 
  3 & 1 & 3 & 0 & 1 & 2 \\ 
  4 & 2 & 7 & 1 & 0 & 1 \\ 
  5 & 0 & 1 & 2 & 1 & 0 \\ 
   \hline
\end{tabular}
\caption{Number of same edges between all decoration pairwise comparisons} 
\label{Test_table_2}
\end{table}

@@

\begin{table}[H]
\begin{minipage}{.45\textwidth}
\centering
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:47 2020
\begin{tabular}{rrrrrr}
  & 1 & 2 & 3 & 4 & 5 \\ 
 1 & 0 & 2 & 3 & 4 & 2 \\ 
  2 & 2 & 0 & 5 & 7 & 3 \\ 
  3 & 3 & 5 & 0 & 4 & 3 \\ 
  4 & 4 & 7 & 4 & 0 & 3 \\ 
  5 & 2 & 3 & 3 & 3 & 0 \\ 
  \end{tabular}

\captionof{table}{Common nodes table}
\end{minipage}
\begin{minipage}{.45\textwidth}
\centering
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Thu Nov 26 18:04:47 2020
\begin{tabular}{rrrrrr}
  & 1 & 2 & 3 & 4 & 5 \\ 
 1 & 0 & 0 & 1 & 2 & 0 \\ 
  2 & 0 & 0 & 3 & 7 & 1 \\ 
  3 & 1 & 3 & 0 & 1 & 2 \\ 
  4 & 2 & 7 & 1 & 0 & 1 \\ 
  5 & 0 & 1 & 2 & 1 & 0 \\ 
  \end{tabular}

\captionof{table}{Common edges table}
\end{minipage}
\end{table}

@@

\begin{figure}[H]
\begin{kframe}
\begin{verbatim}
R> library("matlib")
R> par(mfrow=c(1,2))
R> dist.nodes  <- dist(inv(as.matrix(df.same_nodes)))
R> dist.edges  <- dist(inv(as.matrix(df.same_edges)))
R> plot(hclust(dist.nodes), hang = -1, main = "common nodes")
R> plot(hclust(dist.edges), hang = -1, main = "common edges")
\end{verbatim}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/unnamed-chunk-11-1}

\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> par(mfrow=c(2,1))
R> g.compar <- list_nds_compar(lgrph,"type")
R> nds_compar.3.4 <- plot_nds_compar(g.compar, c(3,4),
+                                    doss = system.file("extdata", package = "decorr"))
R> plot(image_read(nds_compar.3.4))
R> g.compar <- list_eds_compar(lgrph,"type")
R> eds_compar.3.4 <- plot_eds_compar(g.compar, c(3,4),
+                                doss = system.file("extdata", package = "decorr"))
R> plot(image_read(eds_compar.3.4))
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-12-1}

\caption{\label{fig:figs}Decoration comparisons between 3 and 4}\label{fig:unnamed-chunk-12}
\end{figure}

>>>>

{\centering \includegraphics[width=\maxwidth]{figure/a_r_t-1}

\caption{\label{fig:figs}Concatenate of 'a', 'r' and 't' graphical units is 'art'}\label{fig:a_r_t}
\end{figure}

@@

\caption{\label{fig:figs}Potential spatial relations between graphical units}\label{fig:unnamed-chunk-1}
\end{figure}

@@

The inventory of decorations is stored in the \code{imgs} dataframe. The field \code{imgs$idf} is the short name of the decoration, useful during statistical analysis. The primary key of each decoration is the concatenate of \code{imgs$site} and \code{imgs$decor}. These keys will allow joints with the other dataframes (\code{nodes} and \code{edges})\\
%
% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:29 2020
\begin{table}[H]
\centering
\begin{tabular}{|p{0.5cm}|p{2.5cm}|p{2.5cm}|p{8.5cm}|}
  \hline
idf & site & decor & img \\ 
  \hline
  1 & Cerro Muriano & Cerro Muriano 1 & Cerro\_Muriano.Cerro\_Muriano\_1.jpg \\ 
    2 & Torrejon Rubio & Torrejon Rubio 1 & Torrejon\_Rubio.Torrejon\_Rubio\_1.jpg \\ 
    3 & Brozas & Brozas & Brozas.Brozas.jpg \\ 
    4 & Zarza de Montanchez & Zarza De Montanchez & Zarza\_de\_Montanchez.Zarza\_De\_Montanchez.jpg \\ 
    5 & Ibahernando & Ibahernando & Ibahernando.Ibahernando.jpg \\ 
   \hline
\end{tabular}
\caption{The studied corpus, the \code{imgs.tsv} dataframe} 
\label{Test_table}
\end{table}

%
The \pkg{decorr} package training dataset is composed by five stelaes decorations drawings \citep{DiazGuardamino10} belonging to the so-called 'Warrior stelae' family -- with about 140 stelae -- dated to the Late Bronze Age of SW Iberian peninsula \citep{Celestino01}. \\
At first the drawings dataset can be checked by using the \code{imgs} dataframe and the \pkg{magick} package (Fig. \ref{fig:timg})
%
\begin{kframe}
\begin{verbatim}
R> # library("magick")
R> pth <- system.file("extdata", package = "decorr")
R> imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
+                     sep="\t", stringsAsFactors = FALSE)
R> lims <- list()
R> for(i in 1:nrow(imgs)){
+    i1 <- image_read(paste0(pth,"\\",imgs[i,"img"]))
+    lbl.txt <- paste0(imgs[i,"idf"],"\n",
+                      imgs[i,"site"],"\n",
+                      imgs[i,"decor"],"\n",
+                      imgs[i,"img"],"\n",
+                      image_info(i1)$width,"*",image_info(i1)$height," px")
+    i1 <- image_annotate(i1,lbl.txt,location = "northwest",
+                         size = 30, color = "red")
+    lims[[length(lims)+1]]<- i1
+  }
R> out.img <- image_append(c(image_append(c(lims[[1]],lims[[2]],lims[[3]])),
+                            image_append(c(lims[[4]],lims[[5]]))),
+                          stack = TRUE)
R> plot(out.img)
\end{verbatim}
\end{kframe}\begin{figure}[H]

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Nodes (from \\code{nodes.csv} dataframe)}"
R> print(xtable::xtable(head(nodes),
+                       caption = caption),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:31 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 & personnage & 349.81 & -298.32 \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   2 & casque & 349.81 & -243.99 \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 & lance & 238.46 & -298.32 \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   4 & bouclier & 446.02 & -381.17 \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   5 & peigne & 283.00 & -358.01 \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   7 & sexe\_masculin & 342.69 & -427.49 \\ 
   \hline
\end{tabular}
\caption{Nodes (from \code{nodes.csv} dataframe)}} 
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Edges (from \\code{edges.csv} dataframe)}"
R> print(xtable::xtable(head(edges),
+                 caption=caption,
+                 label="edgesdf"),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:31 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrl}
  \hline
 & site & decor & a & b & type \\ 
  \hline
1 & Cerro Muriano & Cerro Muriano 1 &   1 &   4 & = \\ 
  2 & Cerro Muriano & Cerro Muriano 1 &   1 &   5 & = \\ 
  3 & Cerro Muriano & Cerro Muriano 1 &   3 &   5 & = \\ 
  4 & Cerro Muriano & Cerro Muriano 1 &   1 &   2 & + \\ 
  5 & Cerro Muriano & Cerro Muriano 1 &   1 &   7 & + \\ 
  6 & Cerro Muriano & Cerro Muriano 1 &   3 &   1 & = \\ 
   \hline
\end{tabular}
\caption{Edges (from \code{edges.csv} dataframe)}} 
\label{edgesdf}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> lgrph <- list_dec(imgs,nodes,edges,var="type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in list\_dec(imgs, nodes, edges, var = "{}type"{}): unused argument (var = "{}type"{})}}\begin{verbatim}
R> plot(lgrph[[1]],
+       vertex.color = "orange",
+       vertex.frame.color="orange",
+       vertex.label.color = "black",
+       vertex.size = 8,
+       vertex.label.cex = 0.6,
+       edge.color = "orange",
+       vertex.label.family="Helvetica"
+  )
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot(lgrph[[1]], vertex.color = "{}orange"{}, vertex.frame.color = "{}orange"{}, : object 'lgrph' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> # library(decorr)
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".shp",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(nds.df[6,],
+                       # caption="Sixth node (GU 6) of the Torrejon Rubio 1 decoration",
+                       label="nd",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:35 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrlrr}
  \hline
 & site & decor & id & type & x & y \\ 
  \hline
13 & Torrejon Rubio & Torrejon Rubio 1 &   6 & epee & 366.70 & -563.14 \\ 
   \hline
\end{tabular}
\label{nd}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(eds.df[1,],
+                       # caption="First edge of the Torrejon Rubio 1 decoration, the proximity between the sword (GU 6) and the fibula (GU 5)",
+                       label="eds.df",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Dec 04 10:36:35 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrlrrrr}
  \hline
 & site & decor & a & b & type & xa & ya & xb & yb \\ 
  \hline
9 & Torrejon Rubio & Torrejon Rubio 1 &   6 &   5 & = & 366.70 & -563.14 & 490.12 & -513.24 \\ 
   \hline
\end{tabular}
\label{eds.df}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> # library("decorr")
R> par(mar=c(0,0,0,0))
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> img.graph <- plot_dec_grph(nodes = nds.df,
+                             edges = eds.df,
+                             site = sit,
+                             decor = dec,
+                             doss = system.file("extdata", package = "decorr"),
+                             lbl.txt = "type",
+                             lbl.size=2)
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_dec\_grph(nodes = nds.df, edges = eds.df, site = sit, decor = dec, : unused argument (lbl.txt = "{}type"{})}}\begin{verbatim}
R> plot(image_trim(img.graph))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in assert\_image(image): object 'img.graph' not found}}\end{kframe}

@@

The \code{plot_nds_compar()}and \code{plot_eds_compar()} functions create a \code{.png} image of two or more decorations plotted side-by-side with common nodes or edges identified and returns the names of the images. The common edges or nodes are displayed in red by default.
Let us choose the decorations \code{1} (Cerro Muriano 1) and \code{4} (Zarza de Montsanchez) and identify common edges.

\begin{kframe}
\begin{verbatim}
R> # par(mar=c(0,0,0,0))
R> g.compar <- list_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in utils::combn(1:length(lgrph), 2): object 'lgrph' not found}}\begin{verbatim}
R> eds_compar <- plot_compar(g.compar, c(1,4),
+                            focus = "edges",
+                            doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_compar(g.compar, c(1, 4), focus = "{}edges"{}, doss = system.file("{}extdata"{}, : object 'g.compar' not found}}\begin{verbatim}
R> plot(magick::image_trim(magick::image_read(eds_compar)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in magick::image\_read(eds\_compar): path must be URL, filename or raw vector}}\end{kframe}

The comparison shows that \code{1} (Cerro Muriano 1) and \code{4} (Zarza de Montsanchez) decorations have two (2) common edges: \code{lance -=- personnage} and \code{personnage -=- bouclier}.

@@

\begin{kframe}
\begin{verbatim}
R> df.same_edges <- same_neds(lgrph, "type", "edges")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in same\_neds(lgrph, "{}type"{}, "{}edges"{}): could not find function "{}same\_neds"{}}}\begin{verbatim}
R> caption <- "Number of same edges between all decoration pairwise comparisons"
R> print(xtable::xtable(df.same_edges,
+                       caption = caption,
+                       label = "Test_table_2",
+                       size = 8,
+                       digits = c(0)),
+        table.placement="H",
+        include.rownames = TRUE)
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable::xtable(df.same\_edges, caption = caption, label = "{}Test\_table\_2"{}, : object 'df.same\_edges' not found}}\end{kframe}

@@

\begin{table}[H]
\begin{minipage}{.45\textwidth}
\centering
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in same\_neds(lgrph, "{}type"{}, "{}edges"{}): could not find function "{}same\_neds"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in same\_neds(lgrph, "{}type"{}, "{}nodes"{}): could not find function "{}same\_neds"{}}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(df.same\_nodes, digits = c(0)): object 'df.same\_nodes' not found}}\end{kframe}
\captionof{table}{Common nodes table}
\end{minipage}
\begin{minipage}{.45\textwidth}
\centering
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(df.same\_edges, digits = c(0)): object 'df.same\_edges' not found}}\end{kframe}
\captionof{table}{Common edges table}
\end{minipage}
\end{table}

@@

\begin{figure}[H]
\begin{kframe}
\begin{verbatim}
R> library("matlib")
R> par(mfrow=c(1,2))
R> dist.nodes  <- dist(inv(as.matrix(df.same_nodes)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.matrix(df.same\_nodes): object 'df.same\_nodes' not found}}\begin{verbatim}
R> dist.edges  <- dist(inv(as.matrix(df.same_edges)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.matrix(df.same\_edges): object 'df.same\_edges' not found}}\begin{verbatim}
R> plot(hclust(dist.nodes), hang = -1, main = "common nodes")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hclust(dist.nodes): object 'dist.nodes' not found}}\begin{verbatim}
R> plot(hclust(dist.edges), hang = -1, main = "common edges")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hclust(dist.edges): object 'dist.edges' not found}}\end{kframe}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> par(mfrow=c(2,1))
R> g.compar <- list_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in utils::combn(1:length(lgrph), 2): object 'lgrph' not found}}\begin{verbatim}
R> nds_compar.3.4 <- plot_nds_compar(g.compar, c(3,4),
+                                    doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_nds\_compar(g.compar, c(3, 4), doss = system.file("{}extdata"{}, : could not find function "{}plot\_nds\_compar"{}}}\begin{verbatim}
R> plot(image_read(nds_compar.3.4))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(nds\_compar.3.4): object 'nds\_compar.3.4' not found}}\begin{verbatim}
R> # g.compar <- list_eds_compar(lgrph,"type")
R> eds_compar.3.4 <- plot_eds_compar(g.compar, c(3,4),
+                                doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_eds\_compar(g.compar, c(3, 4), doss = system.file("{}extdata"{}, : could not find function "{}plot\_eds\_compar"{}}}\begin{verbatim}
R> plot(image_read(eds_compar.3.4))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(eds\_compar.3.4): object 'eds\_compar.3.4' not found}}\end{kframe}
